Drivers of fish size in a changing climate

### 2017-10-02 draft.Rnw
make error go away!
try to fix norm figure

% Exponent for std.~metabolism & $n=0.88$ \\
\multicolumn{6}{c}{\textbf{Feeding ecology}} \T\\
Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y$^{-1}$)} \T \\
% Exponent for max.~consumption & $q=0.75$ \\
% Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
% Exponent for clearance rate & $p=0.75$ \\
\multicolumn{6}{c}{\textbf{Oxygen budget}} \T \\

@@

int_m <- 500
int_t <- 500
int_temp <- 50

@@

<< norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}). Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size. Increasing temparture (left panel, purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (right panel).'>>=

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 1)

@@

cowplot::plot_grid(cp,np,nrow=1)
@

>>>>

% Exponent for std.~metabolism & $n=0.88$ \\
\multicolumn{6}{c}{\textbf{Feeding ecology}} \T\\
Consumption rate$^1$ & $ \gamma\Theta $ & \multicolumn{4}{c}{$\frac{h w^{p-q}}{(1/f-1)\tau} (g\cdot y^{-1}$)} \T \\
% Exponent for max.~consumption & $q=0.75$ \\
% Coef.~for maximum consumption rate & $h \approx 20 $g$_{WW}^{1-n}$/yr \\
% Exponent for clearance rate & $p=0.75$ \\
\multicolumn{6}{c}{\textbf{Oxygen budget}} \T \\

@@

int_m <- 1000
int_t <- 500
int_temp <- 50

@@

<< norms, fig.cap='On ecological time-scales, temperature affects size via evolved maturation-reaction norms (\\cite{marty_impact_2011}). Most reaction norms found in nature have a negative slope, meaning for faster growth, maturation occurs at a larger size. Increasing temparture (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (bottom panel).'>>=

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)

@@

cowplot::plot_grid(cp,np,nrow=2)
@
